\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
[experiment] volunteer

\shuqing{Background is longer than real user study.}
As the functionality and effectiveness of scripting mode and remote control mode is rather clear, the former works similar to original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
Here we only validate the usability of privacy extraction mode and conducted a user study.
\shuqing{10 volunteers.}
We invited 10 volunteers to participate, who are unconscious of \tool details.
Before the experiment, we disclose to the volunteers about how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
In order to obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
After the experiment, we introduced to them about our attack, analyze the screen recordings together to make sure their personal data is not at risk.
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

\subsubsection{Result}
After collecting the videos, we analyzed the video both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
At last, there are 63882 pieces of data collected among 10 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim was browsing.
Additionally, some keywords such as \textit{account, username and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

>>>>

\shuqing{Background is longer than real user study.}
As the functionality and effectiveness of scripting mode and remote control mode is rather clear, the former works similar to original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
Here we only validate the usability of privacy extraction mode and conducted a user study.
We invited 10 volunteers to participate, who are unconscious of \tool details.
Before the experiment, we disclose to the volunteers about how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
In order to obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
After the experiment, we introduced to them about our attack, analyze the screen recordings together to make sure their personal data is not at risk.
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

\subsubsection{Result}
After collecting the videos, we analyzed the video both automatically and manually.
During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
At last, there are 94058 pieces of data collected among 10 volunteers.
\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim was browsing.
Additionally, some keywords such as \textit{account, username and password} often appear with users' input data because they are often used as labels of input boxes.
Such keywords are more likely to lead us to user-specific data.
For example, when we searched with \textit{account} as keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
